Legacy Data Confounds Modern Genomics Studies

### 2018-08-29 legacy.tex
updated plots

Thus this mutational signal is heavily enriched in GWAS suspicious SNPs, but residual signal remains in non-significant SNPs, presumably because many rare alleles found in individuals with low-quality data remain unidentifiable using association techniques. \sgcomment{do we excluse singletons? We should quantify how much reduction in signal we see.}
%For this reason, the heterogeneously distributed signal persisted in the 1kGP Japanese even after filtering the variants that were significantly associated to quality. 
The removal of individuals with average mapping quality below 30 successfully removes the *AC${\rightarrow}$*CC signal \sgcomment{How about the others?}.
For population genetic analyses, the removal of low-mapping quality individuals appears preferable to filtering.

@@

\begin{figure}
\includegraphics[width=\hsize,keepaspectratio]{./Figures/ManhattanPlot.jpg}

\caption{Manhattan plot of the -log10 p values for the combined test using the deviations from each population of the 1kGP. 
There are 2007 and 3664 variants that reach p values greater than $ p < 10^{-8}$ and $ p < 10^{-6}$ respectively.
Crosses ( + ) represent SNPs that reach a genome wide significance greater than $ p < 10^{-6}$, the circles ( o ) are SNPs that reached values greater than 20, for clarity we implemented hard ceiling at 20.}
  \label{Manhattan}
\end{figure}

>>>>

Thus this mutational signal is heavily enriched in GWAS suspicious SNPs, but residual signal remains in non-significant SNPs, presumably because many rare alleles found in individuals with low-quality data remain unidentifiable using association techniques. \sgcomment{do we excluse singletons? We should quantify how much reduction in signal we see.}
%For this reason, the heterogeneously distributed signal persisted in the 1kGP Japanese even after filtering the variants that were significantly associated to quality. 
The removal of individuals with average mapping quality below 30 successfully removes the *AC${\rightarrow}$*CC signal observed \sgcomment{How about the others?}.
For population genetic analyses, the removal of low-mapping quality individuals appears preferable to filtering.

@@

\begin{figure}
\includegraphics[width=\hsize,keepaspectratio]{./Figures/ManhattanPlot_adjusted.jpg}

\caption{Manhattan plot of the -log10 p values for the combined test using the deviations from each population of the 1kGP. 
There are 3990 variants that reach p values greater than $ p < 0.01$ after performing a two-stage Benjamini & Hochberg FDR adjustment. 
The circles ( o ) are SNPs that reached values greater than 20, for clarity we implemented hard ceiling at 20.}
  \label{Manhattan}
\end{figure}

\begin{figure}
\includegraphics[width=\hsize,keepaspectratio]{./Figures/AllDeviances.jpg}

\caption{Empirical distribution plots of the sum of deviances grouped by N, the number of populations included. The blue curve is the theoretical null reference chi squared distribution with $N$ degrees of freedom. Note $\sum_i^N  \chi^2_1= \chi^2_N$. The grey dotted line indicated the significance level of $10^{-5}$ for the respective distribution which happens to be very close to the adjusted p value threshold at 0.01 FDR. }
  \label{Manhattan}
\end{figure}
